HW2

### 2017-12-03 hw2/h2.tex
fixed type changed to ^(n-1) not ^N -1
Finished example

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...

@@

\textbf{(Minimum(E(u),E(v))}
\\where E(u) and E(v) are encrypted bitwise
Part 1\\
Party one randomly chooses functionality F=u>v or u<v
He first computes 
\begin{itemize}
	\item for i=1 to l 
	\begin{itemize}
		\item $E_{pk} (u_i * v_i ) \gets SM(E_{pk} (u_i) , E_{pk}(v_i))$
		\\ first party one computes the product of current bit of v and u
		\item if selected F: was u$>$v
		\subitem $W_i \gets E_{pk} (u_i) * E_{pk} (u_i * v_i)^{n-1}$
		\\compute $u_i - u_i*v_i $ if there is any $W_i=1$ we know for i $u_i=1$ \& $v_i=0$
		\item else
		\subitem $W_i \gets E_{pk} (v_i) * E_{pk} (u_i * v_i)^{N-1}$
		\\compute $v_i - u_i*v_i $  if there is any $W_i=1$ we know for i $v_i=1$ \& $u_i=0$
		\item $G_i \gets E_{pk}(u_i \oplus v_i)$
		\\now compute xor of two bits if 0 they're the same so first 1 tells us first different bit
		\item $H_i \gets H_{i-1}^{s_i} * G_i ;$ where $s_i \in Z_n$ and $H_0 = E_{pk}(0)$
		\\now mask the xor based on previous bits and a random number, Hs will be 0 till first 1 then every term past that will be a random value based on $s$ values.
		\item $\Phi_i \gets E_{pk}(-1) * H_i$
		\\shift the domain of by n-1
		\textbf{Not sure what this is for? to mask output for party two? two make sure 1s are 0 and every other value is a random value?}
		\item $L_i \gets W_i * \Phi_i^{t_i}$ where $t_i \in Z_n$
		\\ if $W_i$ is 1 $\Phi_i^{t_i}$ will be 0 thus $L_i$ will be 1 otherwise it will be some random value 
	\end{itemize}
	\item $L' \gets \pi_2(L)$
	\\we permute the output so P2 can't tell anything from indices of bits
	\item send $L'$ to P2
\end{itemize}
Part 2\\
Party two computes
\begin{itemize}
	\item $M \gets D_{sk}(L_i')$
	\\decrypt our Ls
	\item if there exists an $M_i=1$
	\subitem $\alpha \gets 1$
	\item else
	\subitem $\alpha \gets 0$
	\\assign alpha based on L values. If there is a 1 we know the selected F function of P1
	\\is true but not what it is
	\item send $E_{pk}(\alpha)$ to P1
\end{itemize}
Part 3\\
\\if alpha is one function is true 0 false, map that to
\\0 if u is min otherwise 1
\begin{itemize}
	\item if F = $u>v$  
		\subitem $E_{pk}(result) \gets E_{pk}(alpha)$
	\item else	
		\subitem $E_{pk}(result) \gets (E_{pk}(alpha)*E_pk(-1))^N-1$
	\\if F was $u>v$ alpha already has 0 if u is min 1 if v
	\\for the other function we have to subtract 1 and to get 0 if u is minimum 1 otherwise
	\\return $E_pk(result)$
\end{itemize}

@@

\subsection*{\textbf{Example}}

>>>>

%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} % for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
\usepackage{hyperref}
% These packages are all incorporated in the memoir class to one degree or another...

@@

\textbf{(Minimum(E(u),E(v))}
\\where E(u) and E(v) are encrypted bitwise
Part 1\\
Party one randomly chooses functionality F=u>v or u<v
He first computes 
\begin{itemize}
	\item for i=1 to l 
	\begin{itemize}
		\item $E_{pk} (u_i * v_i ) \gets SM(E_{pk} (u_i) , E_{pk}(v_i))$
		\\ first party one computes the product of current bit of v and u
		\item if selected F: was u$>$v
		\subitem $W_i \gets E_{pk} (u_i) * E_{pk} (u_i * v_i)^{n-1}$
		\\compute $u_i - u_i*v_i $ if there is any $W_i=1$ we know for i $u_i=1$ \& $v_i=0$
		\item else
		\subitem $W_i \gets E_{pk} (v_i) * E_{pk} (u_i * v_i)^{N-1}$
		\\compute $v_i - u_i*v_i $  if there is any $W_i=1$ we know for i $v_i=1$ \& $u_i=0$
		\item $G_i \gets E_{pk}(u_i \oplus v_i)$
		\\now compute xor of two bits if 0 they're the same so first 1 tells us first different bit
		\item $H_i \gets H_{i-1}^{s_i} * G_i ;$ where $s_i \in Z_n$ and $H_0 = E_{pk}(0)$
		\\now mask the xor based on previous bits and a random number, Hs will be 0 till first 1 then every term past that will be a random value based on $s$ values.
		\item $\Phi_i \gets E_{pk}(-1) * H_i$
		\\shift the domain of by n-1
		\textbf{Not sure what this is for? to mask output for party two? two make sure 1s are 0 and every other value is a random value?}
		\item $L_i \gets W_i * \Phi_i^{t_i}$ where $t_i \in Z_n$
		\\ if $W_i$ is 1 $\Phi_i^{t_i}$ will be 0 thus $L_i$ will be 1 otherwise it will be some random value 
	\end{itemize}
	\item $L' \gets \pi_2(L)$
	\\we permute the output so P2 can't tell anything from indices of bits
	\item send $L'$ to P2
\end{itemize}
Part 2\\
Party two computes
\begin{itemize}
	\item $M \gets D_{sk}(L_i')$
	\\decrypt our Ls
	\item if there exists an $M_i=1$
	\subitem $\alpha \gets 1$
	\item else
	\subitem $\alpha \gets 0$
	\\assign alpha based on L values. If there is a 1 we know the selected F function of P1
	\\is true but not what it is
	\item send $E_{pk}(\alpha)$ to P1
\end{itemize}
Part 3\\
\\if alpha is one function is true 0 false, map that to
\\0 if u is min otherwise 1
\begin{itemize}
	\item if F = $u>v$  
		\subitem $E_{pk}(result) \gets E_{pk}(alpha)$
	\item else	
		\subitem $E_{pk}(result) \gets (E_{pk}(alpha)*E_pk(-1))^{N-1}$
	\\if F was $u>v$ alpha already has 0 if u is min 1 if v
	\\for the other function we have to subtract 1 and to get 0 if u is minimum 1 otherwise
	\\return $E_pk(result)$
\end{itemize}

@@

\subsection*{\textbf{Example}}
The above algorithm is implemented at: \url{https://github.com/drc14/Secure_Minimum}. The example was generated using the program implemented.

\textbf{Minimum(E(u), E(v))} \\
\textbf{Party 1} \\
Choose random functionality f: u $>$ v \\
For 1 in 3: \\
\indent $E(u_1) = E(1)$ \\
\indent $E(v_1) = E(1)$ \\
\indent $E(u_1 * v_1) =  Secure_Multiplication(E(u_1), E(v_1)) = E(1)$ \\
\indent F: u $>$ v: \\
\indent \indent $W_1 = E(0)$ \\
\indent $G_1 = E(u_1 \oplus v_1) = E(0)$ \\
\indent $H_1 = E(0)$ \\
\indent $\Phi_1 = E(12)$ \\
\indent $L_1 = W_1 * \Phi^(t_1) = E(0) * E(12)^8 = E(5)$ \\
For 2 in 3: \\
\indent $E(u_2) = E(1)$ \\
\indent $E(v_2) = E(0)$ \\
\indent $E(u_2 * v_2) = Secure_Multiplication(E(u_2), E(v_2)) = E(0)$ \\
\indent F: u $>$ v: \\
\indent \indent $W_2 = E(1)$ \\
\indent $G_2 = E(u_2 \oplus v_2) = E(1)$ \\
\indent $H_2 = E(1)$ \\
\indent $\Phi_2 = E(0)$ \\
\indent $L_2 = W_2 * \Phi^(t_2) = E(1) * E(0)^{10} = E(1)$ \\
For 3 in 3: \\
\indent $E(u_3) = E(1)$ \\
\indent $E(v_3) = E(1)$ \\
\indent $E(u_3 * v_3) = Secure_Multiplication(E(u_3), E(v_3)) = E(1)$ \\
\indent F: u $>$ v: \\
\indent \indent $W_3 = E(0)$ \\
\indent $G_3 = E(u_3 \oplus v_3) = E(0)$ \\
\indent $H_3 = E(2)$ \\
\indent $\Phi_3 = E(1)$ \\
\indent $L_3 = W_3 * \Phi^(t_3) = E(0) * E(1)^{2} = E(2)$ \\
$E(L) = E(5, 1, 2)$ \\
$E(L') = E(2, 1, 5)$ \\ \\

\textbf{Party 2} \\
$M = D(E(L')) = [2, 1, 5]$ \\
$\alpha = 1$ because 1 appears in $M$\\
$E(\alpha) = E(1)$ \\ \\
\textbf{Party 1} \\
$F: u > v$ \\
\indent Return $E(\alpha) = E(1)$ \\ \\

\textbf{Party 1} \\
E(u) = BD(E(7)) \\ 
E(v) = BD(E(5)) \\
Minimum\_Index $= Mininimum(E(u), E(v)) = E(1)$ \\
For $i=1$ to 3:
\indent $Gamma_1 = E(v_1 - u_1) * E(r_1) = E(1 - 1) * E(5) = E(5)$ \\
\indent $Gamma_2 = E(v_2 - u_2) * E(r_2) = E(0 - 1) * E(10) = E(9)$ \\
\indent $Gamma_3 = E(v_3 - u_3) * E(r_3) = E(1 - 1) * E(8) = E(8)$ \\
$\Gamma = E(5, 9, 8)$ \\
$\Gamma' = \pi_1(\Gamma) = E(9, 8, 5)$ \\ \\

\textbf{Party 2} \\
\textit{$Min_Index = D(E(Min_Index)) = 1$} \\ 
$M' = E(9, 8, 5)^1 = E(9, 8, 5)$ \\ \\

\textbf{Party 1} \\
$M = \pi^{-1}(M') = E(5, 9, 8)$ \\
$\lambda = M * E(\textit{Min\_Index})^{N - r_i} = E(4, 11, 10)$ \\
$\Gamma = E(u) * \lambda = E(5)$ \\
$E(min(E(u), E(v))) = \Gamma = E(5)$ \\
